---
title: "Indoor Personal Comfort Preferences: Mixed Effects Models"
author: "Tim Kelso"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

```{r libraries}
library(DataExplorer)
library(lme4)
library(nlme)
library(tidyverse)
```
# Background 
## Data source  
Found on kaggle.com (https://www.kaggle.com/datasets/claytonmiller/longitudinal-personal-thermal-comfort-preferences?select=enth_tabular_merged.csv) in a quick search for "longitudinal" data.  

Github: https://github.com/buds-lab/longitudinal-personal-thermal-comfort

Participants (Sex): 17 (10M, 7F)
Age range: 21 to 27
Responses/participant: 13 (min), 112(max)
Duration: 4 weeks


## Data information  
*enth_surveys_renamed.csv*
-user_id:	Unique identifier for each participant  
-yob:	Year of birth  
-sex:	Self-reported sex  
-height:	Height in cm  
-weight:	Weight in kg  
-shoulder_circumference:	Shoulder circumference, in cm  
-years_here:	"How long have you been in Singapore (in years)?"  
-used_weather:	"Can you say that you are used to the weather in Singapore?"  
-satisfaction_weather:	7-point Likert scale, "Can you say that you are satisfied -with the weather in this city (outdoor weather conditions)?"  
-sweating: From 1 to 5, "Do you suffer from sweating in Singapore?"  
-enjoy_ourdoor:	"Do you enjoy being outdoor in Singapore?"  
-outdoor_hr_weekday:	"What is your estimation of your time (hours) spent outdoor (per -day) during the weekdays? (for example 2 hrs)"  
-outdoor_hr_weekend:	"What is your estimation of your time (hours) spent outdoor (per -day) during the weekend? (for example 4 hrs)"  
-hsps: Highly Sensitive Person Scale score  
-swls: Satisfaction With Life Scale score  
-extraversion: Extraversion trait score in a 7-point Likert scale  
-agreeableness:	Agreeableness trait score in a 7-point Likert scale  
-conscientiousness:	Consientiousness trait score in a 7-point Likert scale  
-emotional_stability:	Emotional Stability trait score in a 7-point Likert scale  
-openness_to_experiences:	Openness to New Experiences trait score in a 7-point Likert scale  

*enth_tabular_merged*
-space_id:	Unique location on campus
-building_name:	Campus building name
-air_vel:	Perceived air movement, 9 = "Not Perceived", 11 = "Perceived"
-body_presence:	Wheter the user was wearing the smartwatch or not
-change:	Change location, activity or clothing, 11 = "Yes Change", 10 = "No Change"
-clothing:	Clothing, 8 = "very light", 9 = "Light", 10 = "Medium", 11 = "Heavy"
-comfort:	Overall comfort, 10 = "Comfy", 9 = "Not Comfy"
-heartrate:	Heart rate in bpm
-indoor/outdoor:	Location, 9 = "Outdoor", 11 = "Indoor"
-met:	Metabolic rate, 8 = "resting", 9 = "sitting", 10 = "standing", 11 = "exercising"
-response_speed:	Time in seconds it took to complete the survey
-resting_heartrate:	Resting heart rate in bpm
-thermal:	Thermal preference, 9 = "Warmer", 10 = "No Change", 11 = "Cooler"
-nb_temp:	Near body temperature, at the wrist level, in degree Celsius
-skin_temp:	Skin temperature, at the wrist level, in degree Celsius
-indoor_floor:	Building floor provided by the indoor bluetooth beacons
-indoor_latitude:	Latitude provided by the indoor bluetooth beacons
-indoor_longitude:	Longitude provided by the indoor bluetooth beacons
-co2_indoor:	Indoor CO2 measurement by a fixed sensor in ppm
-voc_indoor:	Indoor Volatile Organic Compound measurement by a fixed sensor in ppm
-pm25_indoor:	Indoor Particulate Matter (PM2.5 - Fine Dust) measurement by a fixed sensor in µg/m3
-noise_indoor:	Indoor Ambient noise levels measurement by a fixed sensor in dB
-0.3um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 0.3 µm diameter
-0.5um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 0.5 µm diameter
-1.0um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 1.0 µm diameter
-10.0um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 10.0 µm diameter
-2.5um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 2.5 µm diameter
-5.0um_count_outdoor:	Outdoor count concentration (particles/100ml) of all particles greater than 5.0 µm diameter
-humidity_outdoor:	Outdoor relative humidity by a weather station in %
-pm1.0_outdoor:	Outdoor estimated mass concentration PM1(ug/m3) for PM1.0
-pm10.0_outdoor:	Outdoor estimated mass concentration PM1(ug/m3) for PM10.0
-pm2.5_outdoor:	Outdoor estimated mass concentration PM1(ug/m3) for PM2.5
-pressure_outdoor	:	Outdoor pressure by a weather station in millibars
-temp_outdoor:	Outdoor temperature by a weather station in degree Celsius
-user_id:	Unique identifier for each participant
-temp_indoor:	Indoor temperature by a fixed sensor in degree Celsius
-light_indoor:	Indoor light level by a fixed sensor in lux
-humidity_indoor:	Indoor relative humidity by a fixed sensor in %

##quick thoughts  
- Does time and/or user Id predict comfort?  
- What are the subjective predictors of comfort (if any)?  
- What are the environmental predictors of comfort (if any)?  
- Do more agreeable people report more comfort?  
- Do more extraverted people report less comfort?  


```{r get_data}
# Get the Data
survey_data <- read_csv("enth_surveys_renamed.csv")
environ_data <- read_csv("enth_tabular_merged.csv")
#make copy of raw data for reference
survey_data_orig <- survey_data
environ_data_orig <- environ_data
```

```{r inspect_survey_data}
head(survey_data)
```

```{r inspect_environ_data}
head(environ_data)
```


# Analysis  
## Tables/Columns of potential interest:  



## Graphs  
```{r graph1_time_vs_comfort, include = TRUE, message = FALSE}
environ_data %>% 
  ggplot(aes(x = time, y = comfort)) +
  geom_count()
```

#Predicting comfort as a function of time and and participant
Comfort is binary (10 = "Comfy", 9 = "Not Comfy") so will need to use logistic regression

```{r analysis1_time_vs_comfort}
fm1 <- environ_data %>% 
  mutate(comfort = case_when(
    comfort == 9 ~ 0,
    comfort == 10 ~ 1
  )) %>% 
  glmer(comfort ~ time + (1 | user_id),
            data = .,
            family = binomial)
summary(fm1)

```

```{r graph2_, include = TRUE, message = FALSE}

```

# Key Takeaways  
-  
-  
-  
- 

# Possible next steps  
-  
-  
-  
-  