---
title: "Boston dataset: Linear Regression"
author: "Tim Kelso"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

```{r libraries}
library(MASS)
library(DataExplorer)
library(tidyverse)
```
# Background 
## Data source

## Data information
CRIM - per capita crime rate by town
ZN - proportion of residential land zoned for lots over 25,000 sq.ft.
INDUS - proportion of non-retail business acres per town.
CHAS - Charles River dummy variable (1 if tract bounds river; 0 otherwise)
NOX - nitric oxides concentration (parts per 10 million)
RM - average number of rooms per dwelling
AGE - proportion of owner-occupied units built prior to 1940
DIS - weighted distances to five Boston employment centres
RAD - index of accessibility to radial highways
TAX - full-value property-tax rate per $10,000
PTRATIO - pupil-teacher ratio by town
B - 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town
LSTAT - % lower status of the population
MEDV - Median value of owner-occupied homes in $1000's

```{r get_data}
# Get the Data
data("Boston") 

#make copy of raw data for reference
Boston_orig <- Boston
```

```{r inspect_data}
head(Boston)
```
# Analysis  
## Tables/Columns of potential interest:  
- crim (per capita crime rate) vs dis (weighted distances to employment centres)  
- age (proportion of units built before 1940) vs dis (weighted distances to employment centres)    
- medv (Median value of owner-occupied homes in $1000's) vs dis (weighted distances to employment centres)  

## Is crime rate higher around Boston's employment centres?  
``` {r graph_crim_dis}
#compare first 5 pairs of variables
Boston %>% 
  ggplot(aes(x = dis, y = crim)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()
```
- There appears to be a relationship between crim and dis, however it is not linear
- Try a log transformation of both variables  

``` {r graph_logcrim_logdis}
#compare first 5 pairs of variables
Boston %>% 
  ggplot(aes(x = log(dis), y = log(crim))) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()
```
- Log transformation of both variables appears to result in a linear relationship  
- Will now test this   


## Age of units vs distance to employment centres  
- Would one expect older homes closer to employment centres? In other words, would urban spread originate from employment centres?
``` {r graph_age_dis}
#compare first 5 pairs of variables
Boston %>% 
  ggplot(aes(x = dis, y = age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()
```
- There could be a linear relationship between dis and age, however it appears that the variance around the mean gets larger as dis increases

``` {r graph_rm_medv}
#compare first 5 pairs of variables
Boston %>% 
  ggplot(aes(x = medv, y = rm)) +
  geom_point() +
  theme_minimal()
```
## Graphs  
```{r graph1_, include = TRUE, message = FALSE}

```


```{r graph2_, include = TRUE, message = FALSE}

```

# Key Takeaways  
-  
-  
-  
- 

# Possible next steps  
-  
-  
-  
-  